%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
% Edited : lzhbrian
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{ #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

%%%
% add by lzhbrian
\newcommand{\resumeSubheadingProject}[2]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \emph{\small#2} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeSubheadingedu}[7]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      ~~\textit{\small#3} \textit{\small#4} & \textit{\small #5} \\
      ~~\textit{\small#6} \textit{\small#7} &\\
    \end{tabular*}\vspace{-5pt}
}
\newcommand{\resumeSubheadinghonor}[3]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} {#2}\\
      ~~\textit{\small#3}\\
    \end{tabular*}\vspace{-5pt}
}
\newcommand{\resumeSubheadinghonortwo}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} {#2}\\
      ~~\textit{\small#3}\\
      ~~\textit{\small#4}\\
    \end{tabular*}\vspace{-5pt}
}
\newcommand{\sectionwithbox}[1]{
  \section{\colorbox[rgb]{0.8,0.8,0.8}{{#1}}}
}
\newcommand{\resumeSubheadinghonorone}[2]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} {#2}\\
    \end{tabular*}\vspace{-5pt}
}
\newcommand{\resumeSubheadingPublication}[1]{
  \vspace{-1pt}\item
      {#1}
    \vspace{-5pt}
}

%%%

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \color{blue}\textbf{\href{http://lzhbrian.me/}{\Large Tzu-Heng Lin (Brian) \small Maker, Hacker, \emph{Creativity drives my life.}}} & 
  Website : \color{blue}\href{http://lzhbrian.me/}{http://lzhbrian.me} \\
  \small~~~~Born in \emph{Taiwan}, Grown up in \emph{Shanghai}, now Studying in \emph{Beijing} (will graduate in 2018) & Email : \href{mailto:lzhbrian@gmail.com}{lzhbrian@gmail.com}\\
  
   ~Currently : Junior student in \emph{Dept.of Electronic Engineering, Tsinghua University} & Mobile : +86-131-2192-9165 \\

   ~\underline{Objective : \emph{Seeking Summer Internship in 2017}} &
   	\color{blue}\href{http://www.linkedin.com/in/lzhbrian}{\textbf{[Linkedin]}}
	\color{blue}\href{http://www.github.com/lzhbrian}{\textbf{[Github]}}
\end{tabular*}

%-----------EDUCATION-----------------
%\section{\colorbox[rgb]{0.8,0.8,0.8}{\makebox(70,10){Education}}}
  \sectionwithbox{Education}
  \resumeSubHeadingListStart
    \resumeSubheadingedu
      {Tsinghua University (Dual Degree)}{Beijing, China}
      {Bachelor of Science in Electronic Information}{GPA: 84/100}{Aug 2014 - June 2018}
      {Bachelor of Business Administration in Management (2nd Degree)}{GPA: 87/100}
  \resumeSubHeadingListEnd

%--------PROGRAMMING SKILLS------------
\sectionwithbox{Technology Skills}
  \resumeSubHeadingListStart
    \item{
      \textbf{Languages}{: Python, C/C++, Matlab, R}
      \hfill
      \textbf{Technologies}{: Git, Hadoop, Weka, MySQL, Tableau}
    }
  \resumeSubHeadingListEnd



%-----------EXPERIENCE-----------------
\sectionwithbox{Experience \& Projects}
  \resumeSubHeadingListStart
  
    \resumeSubheading
      {Tsinghua University \color{blue}\href{http://fi.ee.tsinghua.edu.cn}{[link]}}{Beijing, China}
      {\textbf{Research Assistant} in Future Communication \& Internet Lab}{Apr 2016 - Present (9 mo)}
      \resumeItemListStart

        \resumeItem{Online Video Consumption Behaviors Analysis}{(Finished, Paper submitted)}\\
        \vspace{1mm}
          {- Mining a \underline{TB-scale, 2-Month, 10-Million-User} dataset from an ISP including viewing records of most main Video Content Providers, including Youku, IQIYI, Sohu, LeTV, Tencent, KanKan, etc.}\\
          {- Studied the migratory behaviors of users, found potential migratory reasons.}\\
          {- Responsible for all of the data processing and analysis work.} \\
          {~~~~- Written \underline{hundreds of Hadoop MapReduce programs} in Java and also used Python to process the data.}\\
          {~~~~- Analyzed and Visualized the data using Matlab and R.}\\

        \resumeItem{Online Shopping Behaviors Analysis}{(Finished, Paper submitted)}\\
        \vspace{1mm}
          {- Mining a \underline{30-Day, Million-User-scale} dataset of JD online shopping viewing log.}\\
          {- Discovered unique user behaviors when browsing.} \\
          {- Responsible for most of the data processing and analysis work. (Same as the previous Project)}\\
          
      \resumeItemListEnd
  
    \resumeSubheading
      {Academia Sinica \color{blue}\href{http://mmnet.iis.sinica.edu.tw}{[link]}}{Taipei, Taiwan}
      {\textbf{Summer Research Internship} in Data Insights Research Lab}{Jul 2016 - Aug 2016 (2 mo)}
      \resumeItemListStart
        \resumeItem{Data Mining in Facebook Fan Pages: }\\
        \vspace{1mm}
          {- \href{https://www.sinica.edu.tw/ch}{\emph{Academia Sinica}} is the Top National Academy of Taiwan.}\\
          {- Research in a dataset with more than \underline{200,000 Facebook \emph{Fan Pages}, 28 million \emph{posts} with \emph{like} records} in Taiwan.}\\
          {~~~~- Found patterns in posts and real categories of pages.}\\
          {~~~~- Skills including \emph{Statistics}, \emph{Machine Learning}, \emph{Text Mining}, \emph{Time Series Analysis}.}
        \resumeItem{Volunteer, Data Science in Taiwan Conference} {\color{blue}\href{http://www.datasci.tw}{[link]}} \\
      \resumeItemListEnd

    \resumeSubheading
      {Student Association of Science and Technology, EE, THU
      \color{blue}\href{http://www.eesast.com}{[link]}
      \color{blue}\href{https://github.com/eesast}{[github]}
      }
      {Beijing, China}
      {\textbf{Leader of Web Development}, Tsinghua Teamstyle Programming Competition}{Jul 2015 - May 2016 (9 mo)}
      \resumeItemListStart
        \resumeItem{Web Development: \color{blue}\href{http://github.com/eesast/ts17web}{\textbf{[github repo]}}}\\
        \vspace{1mm}
          {- Led the Web Development Team of \emph{Tsinghua Teamstyle Programming Competition 2016}.}\\
          {~~~~- Built the backend using \href{http://www.yiiframework.com}{\emph{Yii framework} (PHP, MVC)}.}\\
          {~~~~- Designed and Built most data structures using \emph{MySQL}, \emph{phpMyAdmin}.}\\
          {~~~~- Implemented most of the features, including \emph{Register}, \emph{Login}, \emph{Online Battle}, \emph{Forum} and \emph{Code submit}, etc.}\\
          {- Co-work, version control using \emph{Git}. }
      \resumeItemListEnd

    \resumeSubheading
      {THU MakerSpace \color{blue}\href{http://www.thumaker.cn}{[link]}}{Beijing, China}
      {\textbf{Vice President}, 2 years experience in maker field}{Sep 2015 - Present (1.5 yrs)}
      \resumeItemListStart
        \resumeItem{Maker Events and Competitions held weekly: }\\
        \vspace{1mm}
          {- THU MakerSpace is one of the greatest Maker Spaces in China.} \\
          {~~~~- We have received letters from Premier Keqiang Li. \color{blue}\href{http://www.moe.edu.cn/publicfiles/business/htmlfiles/moe/moe_838/201505/186765.html}{\textbf{[press]}}}\\
          {- Led the work of the \underline{\emph{Project Dept}}, the \underline{\emph{Public Relation Dept.}} \& the \underline{\emph{Standing Dept.}} }\\
          {~~~~- Responsible for the Maker Events and Competitions held weekly}\\
          {~~~~- Such as \emph{Arduino Tutorial}, \emph{Processing}, \emph{3D modeling}, \emph{Design thinking} and \emph{Brain Storming} Workshops, etc.} \\
          {- Directed several projects, and also Winners of many Make-a-thons.}\\

      \resumeItemListEnd
      
  \resumeSubHeadingListEnd

% \newpage
  





%--------Competition Projects-----------
\sectionwithbox{Projects in Competitions and Awards}

  \resumeSubHeadingListStart
    \resumeSubheadingProject{PennyRaiser: A smart donation box
        \color{blue}\href{http://www.todayfocus.cn/p/4149.html}{\textbf{[press]}}
        \color{blue}\href{http://bjrb.bjd.com.cn/html/2015-12/07/content_335081.htm}{\textbf{[press]}}
        \color{black} }
        {Apr 2015 - Sep 2015 (3 day; 6 mo)}
        \resumeItemListStart
          \resumeItem{\emph{Tsinghua Maker Challenge 2015}: }{\textbf{Championship}}
          \resumeItem{\emph{China-US Maker Competition 2015}: }{\textbf{3rd Prize, Top 5/300 maker teams from the world} } \\
          \vspace{1mm}
            {- \emph{China-US Maker Competition} is the \underline{biggest Make-a-thon in China \& US}.
            \color{blue}\href{https://www.chinaus-maker.org}{\textbf{[link]}}
            }\\
            {- Role: \underline{\textbf{\emph{Team Leader}}} \& \underline{\textbf{\emph{Software Eng.}}}, won the \underline{5th place out of 300 teams} all over the world in 2015.} \\
            {~~~- Led \& organized the team. Started the project.} \\
            {~~~- \emph{iOS app development} using \emph{Swift} with \emph{Xcode}.} \\
              {~~~~~~- Built features include \emph{TableView present}, \emph{SideMenu}, \emph{Customized Tab Button}, \emph{Customized Segue Effect}.} \\
              {~~~~~~- Implemented \emph{QR Code} support which could connect mobile devices with the hardware.} \\
            {~~~- \emph{Design}, \emph{3D modeling}, \emph{3D printing} and \emph{Laser cutting} to build to whole prototype.}
        \resumeItemListEnd


    \resumeSubheadingProject{ITE: Your personal 'kids-can-program' phone companion
        \color{blue}\href{https://mp.weixin.qq.com/s?__biz=MzA5MzMzODQzMQ==\&mid=2650612087\&idx=1\&sn=12fdb18a73edf403c69fd807c391184a\&mpshare=1\&scene=1\&srcid=0117G3nq1r4Pv0uqSLEmG3oy}{\textbf{[post]}}
        \color{black} }
        {May 2016 - May 2016 (3 day)}
        \resumeItemListStart
          \resumeItem{\emph{Tsinghua Maker Challenge 2016}: }{\textbf{Championship}} \\
          \vspace{1mm}
            {- \emph{Tsinghua Maker Challenge} is the \underline{biggest Make-a-thon held in Tsinghua}.}\\
            {- Role: \underline{\textbf{\emph{Team Leader}}} \& \underline{\textbf{\emph{Software Eng.}}}, won the \underline{Championship} in 2016.} \\
            {~~~- Led \& organized the team. Started the project.} \\
            {~~~- \emph{iOS app development} using \emph{Swift} with \emph{Xcode}.} \\
              {~~~~~~- Built features include \emph{TableView present}, \emph{Customized Tab Button}, \emph{Customized Segue Effect}.} \\
              {~~~~~~- Integrated open-sourced-project using \emph{CocoaPods}} \\
        \resumeItemListEnd

    \resumeSubheadingProject{A gameAI for Tsinghua Teamstyle Programming Contest 2015}
        {Apr 2015 - May 2015 (1 mo)}
        \resumeItemListStart
          \resumeItem{\emph{Tsinghua Teamstyle Programming Contest 2015}: }{\textbf{3rd Prize}} \\
          \vspace{1mm}
            {- \emph{Tsinghua Teamstyle Programming Contest} is \underline{one of the biggest programming competitions} in Tsinghua.} \\
            {- Role: \underline{\textbf{\emph{Team Leader}}}, won the \underline{3rd Prize} in 2015.} \\
            {~~~- Led the team.} \\
            {~~~- Developed strategies and implemented using C++. Wrote AI to run a MOBA-style game.}
        \resumeItemListEnd

  \resumeSubHeadingListEnd










%--------SELECTED HONORS------------
\sectionwithbox{Selected Honors}
  \resumeSubHeadingListStart
    \resumeSubheadinghonor
      {Maker Representative}{, Tsinghua Universtiy \color{blue}\href{http://lzhbrian.me/posts_figure/maker.jpeg}{\textbf{[picture]}}}
      {Honored this title by the contributions \& achievements in the maker field.}
    
     \resumeSubheadinghonor
      {1st Prize Scholarship for Taiwanese Student}{, Minister of Education, P.R.C.}
      {\underline{Top 3/50}, Awarded 1st prize scholarship honor for Taiwanese students studying in Mainland China.}

     \resumeSubheadinghonortwo
      {Zheng Geru Scholarship for Comprehensive Performance}{, Tsinghua University}
      {\underline{Top 35/260}, for students who have achieved multiple individual scholarships.}
      {Including excellence scholarships for: \underline{\small\textbf{Science and Technology}}, \underline{\small\textbf{Social Work}}, \underline{\small\textbf{Arts and Cultural}}, respectively.}
    
  \resumeSubHeadingListEnd


% %--------SELECTED COMPETITIONS------------
% \sectionwithbox{Selected Competitions Awards}
%   \resumeSubHeadingListStart
%     \resumeSubheadinghonor
%       {Tsinghua Maker Challenge 2015,2016}{ : Consecutive Championships 
        
%   \color{blue}\href{http://bjrb.bjd.com.cn/html/2015-12/07/content_335081.htm}{\textbf{[2015 press]}}
%   \color{blue}\href{https://mp.weixin.qq.com/s?__biz=MzA5MzMzODQzMQ==\&mid=2650612087\&idx=1\&sn=12fdb18a73edf403c69fd807c391184a\&mpshare=1\&scene=1\&srcid=0117G3nq1r4Pv0uqSLEmG3oy}{\textbf{[2016 description]}} 
  
%   }
%       {\underline{Championships of 2015, 2016 respectively}. Tsinghua Maker Challenge is the biggest Make-a-thon held in Tsinghua.}
    
    
%      \resumeSubheadinghonortwo
%       {China-US Maker Competitions Final}{ : 3rd Prize 
%       \color{blue}\href{https://www.chinaus-maker.org}{\textbf{[link]}}
%       \color{blue}\href{http://bjrb.bjd.com.cn/html/2015-12/07/content_335081.htm}{\textbf{[press]}}
%       \color{blue}\href{http://www.todayfocus.cn/p/4149.html}{\textbf{[press]}}
%       }
%       {China-US Maker Competition is the \underline{biggest Make-a-thon in China \& US}}
%       {I led my team and won the \underline{5th place out of about 300 teams} all over the world in 2015.}

%      \resumeSubheadinghonor
%       {Tsinghua Teamstyle Program Contest}{ : 3rd Prize}
%       {A programming competition writing AI for games. I led my team and won the 5th place in 2015.}
    
%   \resumeSubHeadingListEnd



%--------PUBLICATIONS------------
\sectionwithbox{Publications}
  \resumeSubHeadingListStart
	\resumeSubheadingPublication{H.Yan, \textbf{T.Lin}, G.Wang, Y.Li, H.Zheng, D.Jin, and B.Zhao, On Migratory Behavior in Video Consumption, \emph{Conference Paper Submitted}.}
	\resumeSubheadingPublication{H.Yan, \textbf{T.Lin}, C.Gao, Y.Li, and D.Jin, On the Understanding of User Behaviors Over Multiple Video Content Providers, \emph{Journal Paper Submitted}.}
	\resumeSubheadingPublication{H.Yan, Z.Wang, \textbf{T.Lin}, Y.Li, Y.Wang, and D.Jin, Profiling Users by Online Shopping Behaviors, \emph{Conference Poster Paper Submitted}.}
  \resumeSubHeadingListEnd
  
  
%-------------------------------------------
\end{document}
